Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/paper.tex
modify abstract and introduction

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\title{     
  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
  Joint training of classification model and similarity model for low-resource
  text classification in chatbot
}

\begin{document}
  \maketitle

  \begin{abstract}
    Task-specific  chatbot systems have gained many important applications, such
    as  Siri,  Google home, and customer service systems. In these applications,
    one  of  the  core  problems is the intention detection from a user's input.
    Then,  the  intention  with  its  associated  information  is  mapped into a
    predefined dialog logic graph, and the chatbot returns corresponding answer.
    This  is  the  main  difference  from  a  free chatbot system. The intention
    detection,  assuming  only  one  intention  in  a  user's input here, can be
    modeled  as  a  short  text  classification.  In  practice,  the  number  of
    intentions  can  be hundreds of thousands, as opposed to a few number in the
    traditional text classification problem; enough training data is not trivial
    to be filtered out and labeled from tons of raw user logs with miscellaneous
    information, and generally only 10 to 20 samples per intention are available
    in  the  early  stage.  Then,  how  to  train  an  efficient model in such a
    practical  and important application is critical. In this work, we propose a
    novel  model, called similarity model fused with classification Model (SFC),
    which  combines  a  classification  model  and  a similarity model, and also
    borrows  the  power  of  multi-task  training  as well. We conduct extensive
    experiments  on  4  public  and 1 private datasets. The experimental results
    show that our new model outperforms very strong baselines, BERT, RoBERTa and
    ALBERT based pretrained models by 2 percentages in average accuracy.

@@

  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
  into  many practical products. One typical example is to share the working burden of
  human  customer  service  agents  responsible  for  customers' questions about
  certain  products  or services. Another one is the speech-based control in
  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
  and smart home equipments, to name a few. Regardless of whether these conversations belong to
  single or  multi-round, an essential technique underlying the chatbot is to
  identify  the  real  intention  behind  a  user's  question or reply. Then the
  chatbot  is capable of conducting expected actions, replying texts or accomplishing some
  operations.

  Identifying intention  is  a  challenging task due to some inherent properties. First,
  a customer's  utterance  within  a conversation is usually quite short. Since it
  does  not  contain  enough  information,  short  texts \cite{song2014short} are
  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
  documents,  posing  a  great challenge \cite{chen2019deep} for classification
  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
  sufficient  labeled  data  to  train  a good model. Because developers have to
  examine tons of real system logs for typical user's utterances, and then label
  them  with expected intentions. Therefore, to build a task-specific chatbot with
  high  performance, it is essential to solve the challenge of short-text
  classification   \cite{sriram2010short}   problem   under   few-shot   setting
  \cite{yu2018diverse}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
%% Because html converters don't know tabularnewline
\title{     
  %SFC: Few-Shot Text Classification via Similarity Fused with Classification System
  Joint Training of Classification and Similarity Models for \\ 
  Intention Detection in Task-specific Chatbot
}

\begin{document}
  \maketitle
  \linenumbers

  \begin{abstract}
    Task-specific  chatbot systems have gained many important applications, such
    as  Siri,  Google home, and customer service systems, etc. One essential technique 
    underlying these applications  is to detect the real intention behind a user's input.
    The intention detection,  assuming  only  one  intention  in  a  user's input here, can be
    regarded  as  a  short  text  classification problem.  In  practice,  the  number  of
    intentions  can  be hundreds of thousands, as opposed to a few number in the
    traditional text classification problem; creating enough training data from tons of 
    raw user logs with miscellaneous information is not trivial, 
    and generally only 10 to 20 samples per intention are available in  the  early  stage.  
    Thus,  how  to  train  an  effective short-text classification model with limited training
    example in such a practical  and important application is critical. In this work, we propose a
    novel  model, called similarity model fused with classification model (SFC),
    which  combines  a  classification  model  and  a similarity model, and also
    borrows  the  power  of  multi-task  training  as well. We conduct extensive
    experiments  on  4  public  and 1 private datasets. Experimental results
    show that our new model outperforms very strong baselines (i.e., BERT, RoBERTa and
    ALBERT based pretrained models) by 2 percentages in average accuracy.

@@

  Task-specific  conversational  chatbot  \cite{wen2016network}  has been applied
  into  many practical products. One typical example is the chatbot that shares the working burden of
  human  customer  service  agents  responsible  for  customers' questions about
  certain  products  or services. Another one is the speech-based control in
  devices  like  intelligent  speakers, such as Siri, Google home, Baidu Xiaodu,
  and smart home equipments, to name a few. Regardless of whether these conversations belong to
  single or  multi-round, an essential technique underlying this type of chatbot is to
  identify  the  real  intention  behind  a  user's  question or reply. 
  The detected intention  with  its  associated  information  is then mapped into a
  predefined dialog logic graph, from which a suitable response (e.g., conducting 
  expected actions, replying texts or accomplishing some operations, etc)  is returned.
  This  is  the  main  difference  from  a  free chatbot.

  Intention detection in task-specific chatbot  is  a  challenging task due to some inherent properties. First,
  a customer's  utterance  within  a conversation is usually quite short. Since it
  does  not  contain  enough  information,  short  texts \cite{song2014short} are
  thought  to  be  more  ambiguous  compared to long texts such as paragraphs or
  documents,  posing  a  great challenge \cite{chen2019deep} for classification
  task   \cite{phan2008learning,yan2009dynamic,hua2015short}.   Second,  in  the
  initial  stage  of  building  a  chatbot  , it is often rather hard to collect
  sufficient  labeled  data  to  train  a good model. Because developers have to
  examine tons of real system logs for typical user's utterances, and then label
  them  with expected intentions. Therefore, to build a task-specific chatbot with
  high  performance, it is essential to solve the challenge of short-text
  classification   \cite{sriram2010short}   problem   under   few-shot   setting
  \cite{yu2018diverse}.
